---
title: 'First Experiment: Levels of Offensiveness'
author: "Nicole Birkner"
date: "February 23, 2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyverse)
```

# Importing the data

```{r}
getwd()
data = read.csv("Language Attitudes_February 23, 2020_15.38.csv")
data = data[-1,]
data = data[-1,]
```

# Cleaning up the data

```{r}
new_data = subset(data, Status != "Survey Preview")
new_data = subset(new_data, Q9 != "")
```

```{r}
dim(new_data)
```

```{r}
for(i in 1:length(new_data$Q14_2_TEXT)){
  if(grepl("Spain", as.character(new_data$Q14_2_TEXT[i]), ignore.case=TRUE) == "TRUE"){
    new_data$Q14_2_TEXT[i] = "Spain"
  }
  if(grepl("Èspaña", as.character(new_data$Q14_2_TEXT[i]), ignore.case=TRUE) == "TRUE"){
    new_data$Q14_2_TEXT[i] = "Spain"
  }
  if(grepl("Madrid", as.character(new_data$Q14_2_TEXT[i]), ignore.case=TRUE) == "TRUE"){
    new_data$Q14_2_TEXT[i] = "Spain"
  }
  if(grepl("Mexico", as.character(new_data$Q14_2_TEXT[i]), ignore.case=TRUE) == "TRUE"){
    new_data$Q14_2_TEXT[i] = "Mexico"
  }
}

v <- c()

for(i in 1:length(new_data$Q14_2_TEXT)){
  if(as.character(new_data$Q14[i]) == "USA"){
    v[i] <- "USA"
  }
  if(as.character(new_data$Q14_2_TEXT[i] == "Spain")){
    v[i] <- "Spain"
  }
  if(as.character(new_data$Q14_2_TEXT[i] == "Mexico")){
    v[i] <- "Mexico"
  }
}

for(i in 1:length(v)){
  if(is.na(v[i])){
    v[i] <- "Other"
  }
}

new_data$Merged <- v
```

**Function to normalize data:**

```{r}
normalize_data <- function(data.frame, question, names){
  table <- table(data.frame$Merged, question)
  df <- data.frame(table)
  df
  names(df) <- c("Country", "Answer", "Frequency")
  df <- df %>% filter(Answer=="Not offensive" | Answer=="Slightly offensive"|Answer==
  "Moderately offensive" | Answer=="Very offensive") %>% arrange(desc(Country))
  totals <- matrix(0, ncol=2, nrow=length(names))
  totals.df <- data.frame(totals)
  names(totals.df) <- c("Country", "Total")
  totals.df$Country <- names
  for(i in 1:length(names)){
    filter <- df %>% filter(Country == names[i]) 
    total <- sum(filter$Frequency)
    totals.df$Total[i] <- total
  } 
  percentage.df <- merge(df, totals.df, by="Country")
  percentage.df$Percentage <- percentage.df$Frequency/percentage.df$Total
  percentage.df
}
```

\pagebreak

\newpage

# Initial plots

## Question 1: The Americans shared their opinions in the conference.

```{r}
library(ggplot2)

Q1_data <- new_data %>% filter(Q1!="")
names <- unique(Q1_data$Merged)

Q1_normalized <- normalize_data(Q1_data, Q1_data$Q1, names)
Q1_normalized <- Q1_normalized %>% filter(Percentage!=0)
Q1_normalized

p<-ggplot(Q1_normalized, aes(x=factor(Answer, levels=c("Extremely offensive", 
  "Moderately offensive", "Slightly offensive", "Not offensive")), 
   y=Percentage, fill=Country)) + geom_bar(stat="identity", position=position_dodge())

p + labs(title="Question 1", 
  subtitle="The Americans shared their opinions in the conference.") + 
  xlab("Rank") + ylab("Normalized Percentage")
```

\pagebreak

\newpage

## Question 2: We could not be seated at the restaurant. It was flooded with Gringos.

```{r}
Q2_data <- new_data %>% filter(Q2!="")
names <- unique(Q2_data$Merged)

Q2_normalized <- normalize_data(Q2_data, Q2_data$Q2, names)
Q2_normalized <- Q2_normalized %>% filter(Percentage!=0)
Q2_normalized

p<-ggplot(Q2_normalized, aes(x=factor(Answer, levels=c("Extremely offensive", 
  "Moderately offensive", "Slightly offensive", "Not offensive")), 
  y=Percentage, fill=Country)) + geom_bar(stat="identity", position=position_dodge())

p + labs(title = "Question 2", 
  subtitle = "We could not be seated at the restaurant. It was flooded with Gringos.") + 
  xlab("Rank") + ylab("Normalized Percentage")
```

\pagebreak

\newpage

## Question 3: The Americans interrupted with their opinions in the conference.

```{r}
Q3_data <- new_data %>% filter(Q3!="")
names <- unique(Q3_data$Merged)

Q3_normalized <- normalize_data(Q3_data, Q3_data$Q3, names)
Q3_normalized <- Q3_normalized %>% filter(Percentage!=0)
Q3_normalized

p<-ggplot(Q3_normalized, aes(x=factor(Answer, levels=c("Extremely offensive", 
  "Moderately offensive", "Slightly offensive", "Not offensive")), 
  y=Percentage, fill=Country)) + geom_bar(stat="identity", position=position_dodge())

p + labs(title="Question 3", 
  subtitle="The Americans interrupted with their opinions in the conference.") + 
  xlab("Rank") + ylab("Normalized Percentage")
```

\pagebreak

\newpage

## Question 4: We could not be seated at the restaurant. It was filled with Gringos.

```{r}
Q4_data <- new_data %>% filter(Q4!="")
names <- unique(Q4_data$Merged)

Q4_normalized <- normalize_data(Q4_data, Q4_data$Q4, names)
Q4_normalized <- Q4_normalized %>% filter(Percentage!=0)
Q4_normalized

p<-ggplot(Q4_normalized, aes(x=factor(Answer, levels=c("Extremely offensive", 
   "Moderately offensive", "Slightly offensive", "Not offensive")), 
   y=Percentage, fill=Country)) + geom_bar(stat="identity", position=position_dodge())

p + labs(title="Question 4", 
  subtitle="We could not be seated at the restaurant. It was filled with Gringos.") + 
  xlab("Rank") + ylab("Normalized Percentage")
```

\pagebreak

\newpage

## Question 5: The Gringos shared their opinions in the conference.

```{r}
Q5_data <- new_data %>% filter(Q5!="")
names <- unique(Q5_data$Merged)

Q5_normalized <- normalize_data(Q5_data, Q5_data$Q5, names)
Q5_normalized <- Q5_normalized %>% filter(Percentage!=0)
Q5_normalized

p<-ggplot(Q5_normalized, aes(x=factor(Answer, levels=c("Extremely offensive", 
  "Moderately offensive", "Slightly offensive", "Not offensive")), 
  y=Percentage, fill=Country)) + geom_bar(stat="identity", position=position_dodge())
p + labs(title="Question 5", 
  subtitle="The Gringos shared their opinions in the conference.") + 
  xlab("Rank") + ylab("Normalized Percentage")
```

\pagebreak

\newpage

## Question 6: We could not be seated at the restaurant. It was flooded with Americans.

```{r}
Q6_data <- new_data %>% filter(Q6!="")
names <- unique(Q6_data$Merged)

Q6_normalized <- normalize_data(Q6_data, Q6_data$Q6, names)
Q6_normalized <- Q6_normalized %>% filter(Percentage!=0)
Q6_normalized

p<-ggplot(Q6_normalized, aes(x=factor(Answer, levels=c("Extremely offensive", 
  "Moderately offensive", "Slightly offensive", "Not offensive")), 
  y=Percentage, fill=Country)) + geom_bar(stat = "identity", position = position_dodge())

p + labs(title = "Question 6", 
  subtitle = "We could not be seated at the restaurant. It was flooded with Americans.") + 
  xlab("Rank") + ylab("Normalized Percentage")
```

\pagebreak

\newpage

## Question 7: The Gringos interrupted with their opinions in the conference.

```{r}
Q7_data <- new_data %>% filter(Q7!="")
names <- unique(Q7_data$Merged)

Q7_normalized <- normalize_data(Q7_data, Q7_data$Q7, names)
Q7_normalized <- Q7_normalized %>% filter(Percentage!=0)
Q7_normalized

p<-ggplot(Q7_normalized, aes(x=factor(Answer, levels=c("Extremely offensive", 
  "Moderately offensive", "Slightly offensive", "Not offensive")), 
  y=Percentage, fill=Country)) + geom_bar(stat="identity", position=position_dodge())

p + labs(title="Question 7", 
  subtitle="The Gringos interrupted with their opinions in the conference.") + 
  xlab("Rank") + ylab("Normalized Percentage")
```

\pagebreak

\newpage

## Question 8: We could not be seated at the restaurant. It was filled with Americans.

```{r}
Q8_data <- new_data %>% filter(Q8!="")
names <- unique(Q8_data$Merged)

Q8_normalized <- normalize_data(Q8_data, Q8_data$Q8, names)
Q8_normalized <- Q8_normalized %>% filter(Percentage!=0)
Q8_normalized

p<-ggplot(Q8_normalized, aes(x=factor(Answer, levels=c("Extremely offensive", 
  "Moderately offensive", "Slightly offensive", "Not offensive")), 
  y=Percentage, fill=Country)) + geom_bar(stat="identity", position=position_dodge())

p + labs(title="Question 8", 
  subtitle="We could not be seated at the restaurant. It was filled with Americans.") + 
  xlab("Rank") + ylab("Normalized Percentage")
```

